Advanced Normalization Tools (ANTS)

### 2010-03-30 Documentation/Tex/ants.tex
update with some warp info
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@456 fd2da0a4-d968-48df-9cb5-d8c496287cbf

$L~M~N$  is the center of rotation .

@@

\subsubsection{Deformation Field File}
ANTS writes the deformation field using one file for the deformation in each dimension. 
For example, if the deformation field is named ABCD.nii.gz and exists in three dimensions, the corresponding files are:
ABCDxvec.nii.gz, 
ABCDyvec.nii.gz, 
ABCDzvec.nii.gz (for 3D).  Note that ANTS programs {\em assume} the $*$vec part of the name will exist.  Thus, 
one refers to the warp file as  ABCD.nii.gz , dropping the $*$vec from the name. 
\subsubsection{Labeled Point Sets}
There are three formats supported
\begin{itemize}
\item  VTK format: point + scalar label in a .vtk file. {\bf FIXME NEED MORE DETAIL -- what type of vtk data ?  polydata?}.
\item  Labeled point sets are saved as an image volume with the intensity = 1,2,3 for label = 1,2,3. For example, 
figure~\ref{fig:frown} shows 2D images representing a 3-class labeled point set. 
\item Avants Format. In this simple format, the point sets are saved as a text file. The first and last line is always 0 0 0 0. Each line in between for a point as X Y Z L (L is the label.)
\end{itemize}
The names and formats of the output files are both specified by -o option to the ANTS executable. 
For example, for in 3D with -o RegA2B.nii.gz , the typical output files are:
Affine transform file: 
RegA2BAffine.txt 
Warping deformation field: 
RegA2BWarpxvec.nii.gz, RegA2BWarpyvec.nii.gz, RegA2BWarpzvec.nii.gz
Inverse warping deformation field:
RegA2BInverseWarpxvec.nii.gz, RegA2BInverseWarpyvec.nii.gz, RegA2BInverseWarpzvec.nii.gz.  
To apply the affine transform and the deformation field to the moving image, use WarpImageMultiTransform. 
For example: to apply the transform to the moving image:

>>>>

$M~N~O$  is the center of rotation .

@@

\subsubsection{Deformation Field File}
ANTS writes the deformation field using one file for the deformation in each dimension. 
For example, if the deformation field is named ABCD.nii.gz and exists in three dimensions, the corresponding files are:
ABCDxvec.nii.gz, 
ABCDyvec.nii.gz, 
ABCDzvec.nii.gz (for 3D).  Note that ANTS programs {\em assume} the $*$vec part of the name will exist.  Thus, 
one refers to the warp file as  ABCD.nii.gz , dropping the $*$vec from the name. 
The displacement for each voxel is defined in physical image space.  If you want to 
see the details of how a warp is achieved, look at the code in itkWarpImageMultiTransform.txx. 
One issue to be aware of is that if you are directly indexing a vector component image in 
voxel coordinates, then you need to apply the image's direction matrix to the vector.  
An example of this is in ANTSJacobian.cxx, the TransformVector function.

\subsubsection{Labeled Point Sets}
There are three formats supported
\begin{itemize}
\item  VTK format: point + scalar label in a .vtk file. {\bf FIXME NEED MORE DETAIL -- what type of vtk data ?  polydata?}.
\item  Labeled point sets are saved as an image volume with the intensity = 1,2,3 for label = 1,2,3. For example, 
figure~\ref{fig:frown} shows 2D images representing a 3-class labeled point set. 
\item Avants Format. In this simple format, the point sets are saved as a text file. The first and last line is always 0 0 0 0. Each line in between for a point as X Y Z L (L is the label.)
\end{itemize}
The names and formats of the output files are both specified by -o option to the ANTS executable. 
For example, for in 3D with -o RegA2B.nii.gz , the typical output files are:
Affine transform file: 
RegA2BAffine.txt 
Warping deformation field: 
RegA2BWarpxvec.nii.gz, RegA2BWarpyvec.nii.gz, RegA2BWarpzvec.nii.gz
Inverse warping deformation field:
RegA2BInverseWarpxvec.nii.gz, RegA2BInverseWarpyvec.nii.gz, RegA2BInverseWarpzvec.nii.gz.  
To apply the affine transform and the deformation field to the moving image, use WarpImageMultiTransform. 
For example: to apply the transform to the moving image:
